%Provide a high-level overview of the secure hybrid pipeline you engineered.
%• Identify the specific cryptographic primitives utilized for the three core phases: Bulk Data Transfer, Asymmetric Key Exchange, and Identity Authentication.
%• Briefly state how your implementation satisfies the foundational goals of Confidentiality, Integrity, and Authenticity.
\section{Executive Summary}
\par The hybrid cryptographic pipeline created for this project uses both symmetric and asymmetric cryptography to establish a secure channel of communication over an insecure channel. This is done across three phases: the Bulk Data Transfer phase, Asymmetric Key Exchange phase, and Identity Authentication phase. The latter two phases are used to establish the secure channel, while the former is used to communicate across the established channel.
\par The Bulk Data Transfer phase uses AES-256 in Galois/Counter Mode (AES-256-GCM) to encrypt communications with a shared symmetric encryption key. In addition to encrypting messages, AES-256 in GCM mode also produces an authentication tag that can be used to detect if a message was altered in transit. The symmetric key used to encrypt and decrypt messages is distributed in the asymmetric key exchange phase.
\par The Asymmetric Key Exchange phase uses Elliptic Curve Diffie-Hellman Key Exchange (ECDH) and HKDF to distribute a shared secret key between parties without sending it in plaintext across the insecure channel. Specifically, both the sender and receiver generate ephemeral X25519 keypairs, and send their public key to the other party. Then each party takes their own private key and the other party’s public key and uses them to derive a shared secret. Finally, both parties pass the shared secret through HKDF with identical parameters to create a key suitable for use with as an AES-256 encryption key.
\par The Identity Authentication phase is used to validate that the X25519 public key received by one party was created by the other party and not a man in the middle. This is done using a Probabilistic signature scheme that leverages RSA-2048 asymmetric encryption keys (RSA-2048-PSS). Each party uses the private component of its own persistent RSA-2048 key-pair to create a digital signature sent alongside the X25519 public key. The receiver then verifies that the digital signature is valid for the received X25519 using their pre-shared RSA-2048 public key.
 My implementation provides Confidentiality and Integrity are provided by encrypting messages using AES-256 in Galois/Counter Mode (AES-256-GCM). This mode both encrypts the bulk data and generates an authentication tag that catches changes to the ciphertext. Finally, the use of RSA-2048-PSS provides authenticity, as it stops a man in the middle from impersonating one of the involved parties.

